Exploratory Analysis

### 2023-11-30 Code/Draft1Rmd.Rmd
jsjsjs
Updated line plot

>>>>

```{r}
#Create individual data sets for Oregon, Washington, and California
or_health_ranking <- health_ranking[health_ranking$state == "Oregon",]
ca_health_ranking <- health_ranking[health_ranking$state == "California",]
wa_health_ranking <- health_ranking[health_ranking$state == "Washington",]

#Now create yearly averages for the states from the healthrank_to_yearly function from Functions.R:
or_yearly <- healthrank_to_yearly(or_health_ranking)
ca_yearly <- healthrank_to_yearly(ca_health_ranking)
wa_yearly <- healthrank_to_yearly(wa_health_ranking)

ggplot()+
  geom_line(data = or_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Oregon")) +
  geom_line(data = ca_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "California")) +
  geom_line(data = wa_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Washington")) +
  scale_color_manual(name = "State",
                     values = c("Oregon" = "blue", "California" = "red", "Washington" = "green")) +
  theme_bw()
```
